### 2019-04-03 papers/journal/abstract.tex
Updated dia and results fix

Vesicle Traffic Systems (VTSs) are the material transport 
mechanisms among the compartments inside the biological cells.
%
The compartments are viewed as nodes that are labeled with the
containing chemicals and the transport channels
are similarly viewed as labeled edges between the nodes.
%
Understanding VTSs is an ongoing area of research and for many cells
they are partially known.
%
For example, there may be undiscovered edges, nodes, or their labels
in a VTS of a cell.
%
It has been speculated that there are properties that the VTSs must
satisfy.
%
For example, stability, i.e., every chemical that is leaving a
compartment comes back.
%
Many synthesis questions may arise in this scenario, where we want
to complete a partially known VTS under a given property.
%
In the paper, we present novel encodings of the above questions
into the QBF (quantified Boolean formula) satisfiability problems.
%
We have implemented the encodings in a highly configurable tool
and applied to a couple of found-in-nature VTSs and 
several synthetic graphs.
%
Our results demonstrate that our method can scale up to the graphs of interest.

% Vesicle Traffic Systems(VTSs) are the material transport 
% mechanisms among the compartments inside the biological cells.

>>>>

Vesicle Traffic Systems (VTSs) transport cargo among the intracellular compartments of eukaryotic biological cells.
%
The compartments are viewed as nodes that are labeled by their chemical identity and the transport vesicles are similarly viewed as labeled edges between the nodes.
%
Several interesting questions about VTSs translate to combinatorial search and synthesis problems. 
%
We present novel SAT, SMT and QBF based encodings of the properties over vesicle traffic systems.
%
We have implemented the presented encoding in a tool that searches for the networks that satisfy properties related to transport consistency conditions using these solvers. 
%
In our numerical experiments, we show that our tool can search for networks of sizes that are relevant to real cellular systems.
%
Understanding VTSs is an ongoing area of
research and for many cells they are partially known. 
%
For example, there
may be undiscovered edges, nodes, or their labels in a VTS of a cell. 
%
It has been speculated that there are properties that the VTSs must satisfy.
For example, stability, i.e., every chemical that is leaving a compartment
comes back. 
%
Many synthesis questions may arise in this scenario, where
we want to complete a partially known VTS under a given property.
%
In the paper, we present novel encodings of the above questions into
the QBF (quantified Boolean formula) satisfiability problems. 
%
We have implemented the encodings in a highly configurable tool and applied to a
couple of found-in-nature VTSs and several synthetic graphs.
%
Our results demonstrate that our method can scale up to the graphs of interest.
% Vesicle Traffic Systems(VTSs) are the material transport 
% mechanisms among the compartments inside the biological cells.

### 2019-04-03 papers/journal/synth-table.tex
results update
Updated dia and results fix

		plos1-dia[3C]& 0.02 &$\infty$& 0.37 &$\infty$& 0.46 & $\infty$ & 0.63 &$\infty$& 0.21 & -1 E, -1AE, -1AN. +1E, +1N. \\\hline
		plos2-dia[4C] & 2.02 & 0   & 2.38 & 0  & 4.27  & 0 & 5.94 & 0 &  3.30 & 0 \\\hline
		sub-mammal[3C]  & 4.61 & 1 E  & 5.98 & 5 PE & 27.33 & 1 E & 14.75 & 1 E & 6.82  & -1E, -2PE, -1AN. +1E, +4PE, +4N, +2AN, +2AE. \\\hline
		node4[3C]  & 5.93  & 1 E   &  13.72 & 12 PE  &  5.09  & $\infty$ & 4.30 &$\infty$& 7.21  & -2 E, -2PE, -1 N, -1AN, -1 AE. +12 N, +8E, +1PE.\\\hline
		%   yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
		yeast-graph[3C]   & 105.15    & 2 E  &   247.04  & 15 PE   & 1381.24  & 2 E  & 541.66   & 2 E & 326.09  &  -1E, -1N, -1AE, -1AN, -1PE. +2E, +11PE, +20N. \\\hline
	   	node6[3C]  &  454.98  & 2 E  &  1209.30    & 21 PE    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A \\\hline
		mammal-graph[3C]  &  T/O     & N/A  &  T/O     & N/A    &  T/O         & N/A      &  T/O    &  N/A    &  T/O     & N/A\\\hline
		%    & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
	\end{tabular}
	% \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
	% Time is reported in seconds.}
	% \label{tab:qf-graph}
	% \end{table}
	\begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
		{\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
		{\multirow{2}{*} \textbf{Table b}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
		\cline{2-11}
		{} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\
		\hline

		plos1-dia & 0.04&$\infty$& 0.31 &$\infty$& 0.20 & $\infty$ & 0.27&$\infty$& 3.47 & -1E, -1PE, - 1N, -1PE. +1AE, +1PE, +1N\\\hline
		plos2-dia & 3.97 & 0 &  2.26 & 0  & 5.46 & 0 & 5.35 & 0 & 3.24 & 0 \\\hline
		sub-mammal & 3.22 & 1 E  & 4.18 & 5 PE  & 24.73 & 1 E  & 9.21 & 1 E & 5.36  & -1E, -2PE, -1AN. +1 E, +4PE, +4N, +2AN, +2AE \\\hline
		node4  & 4.01  & 1 E  & 10.19  & 12 PE & 4.26  & $\infty$ & 4.13 &$\infty$&  6.89  & -2 E, -2PE, -1N, -1AN, -1AE. +12N, +8E, +1PE \\\hline
		yeast-graph & 38.68  & 2 E  &   127.45  & 15 PE   & 1002.41  & 2 E  & 434.08   & 2 E & 197.82  &  -1E, -1N, -1AE, -1AN, -1PE. +2E, +11PE, +20N. \\\hline
		node6  &  235.97  & 2 E  &  549.25    & 21 PE    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A \\\hline
		mammal-graph   &  T/O     & N/A  &  T/O    & N/A    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A\\\hline
	\end{tabular}
	\caption{Run-times for synthesis queries. \#C stands for minimum changes in the synthesized VTS in comparison with the given partial VTS. Time is reported in seconds. (a) The solver used is DepQBF (b) The solver used is Z3. The sub-mammal is a subgraph of the complete mammal-graph. In the Add/Delete parts column, ‘+’n sign is used to show the addition of n number of the molecules, similarly ‘-’n is used to show the removal of n number of molecules. In the table, N is node labels, AN is active node molecules, E is edges, PE is molecule presence on the edge and AE is active molecules on the edge. The [kC] stands for k graph connectedness which is part of only DepQBF experiments.}

>>>>

		plos1-dia[3C]& 0.02 &$\infty$& 0.37 &$\infty$& 0.46 & $\infty$ & 0.63 &$\infty$& 0.21 & -1 E, -1AE, -1AN. +1E, +1N. \\\hline
		plos2-dia[4C] & 2.02 & 0   & 2.38 & 0  & 4.27  & 0 & 5.94 & 0 &  3.30 & 0 \\\hline
		sub-mammal[3C]  & 4.61 & 1 E  & 5.98 & 7 PE & 27.33 & 1 E & 14.75 & 1 E & 6.82  & -1E, -2PE, -4AN. +1 E, +5PE, +4N, +3AN, +3AE. \\\hline
		node4[3C]  & 5.93  & 1 E   &  13.72 & 12 PE  &  5.09  & $\infty$ & 4.30 &$\infty$& 7.21  & -2 E, -2PE, -1 N, -1AN, -1 AE. +18N, +8E, +1PE.\\\hline
		%   yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
		yeast-graph[3C]   & 105.15    & 2 E  &   247.04  & 15 PE   & 1381.24  & 2 E  & 541.66   & 2 E & 326.09  &  -1E, -1N, -1AE, -1AN, -1PE. +2E, +11PE, +20N. \\\hline
	   	node6[3C]  &  454.98  & 2 E  &  1209.30    & 21 PE    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A \\\hline
		mammal-graph[3C]  &  T/O     & N/A  &  T/O     & N/A    &  T/O         & N/A      &  T/O    &  N/A    &  T/O     & N/A\\\hline
		%    & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
	\end{tabular}
	% \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
	% Time is reported in seconds.}
	% \label{tab:qf-graph}
	% \end{table}
	\begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
		{\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
		{\multirow{2}{*} \textbf{Table b}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
		\cline{2-11}
		{} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\
		\hline

		plos1-dia & 0.04&$\infty$& 0.31 &$\infty$& 0.20 & $\infty$ & 0.27&$\infty$& 3.47 & -1E, -1PE, - 1N, -1PE. +1AE, +1PE, +1N\\\hline
		plos2-dia & 3.97 & 0 &  2.26 & 0  & 5.46 & 0 & 5.35 & 0 & 3.24 & 0 \\\hline
		sub-mammal & 3.22 & 1 E  & 4.18 & 7 PE  & 24.73 & 1 E  & 9.21 & 1 E & 5.36  & -1E, -2PE, -4AN. +1 E, +5PE, +4N, +3AN, +3AE \\\hline
		node4  & 4.01  & 1 E  & 10.19  & 12 PE & 4.26  & $\infty$ & 4.13 &$\infty$&  6.89  & -2 E, -2PE, -1N, -1AN, -1AE. +18N, +8E, +1PE \\\hline
		yeast-graph & 38.68  & 2 E  &   127.45  & 15 PE   & 1002.41  & 2 E  & 434.08   & 2 E & 197.82  &  -1E, -1N, -1AE, -1AN, -1PE. +2E, +11PE, +20N. \\\hline
		node6  &  235.97  & 2 E  &  549.25    & 21 PE    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A \\\hline
		mammal-graph   &  T/O     & N/A  &  T/O    & N/A    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A\\\hline
	\end{tabular}
	\caption{Run-times for synthesis queries. \#C stands for minimum changes in the synthesized VTS in comparison with the given partial VTS. Time is reported in seconds. (a) The solver used is DepQBF (b) The solver used is Z3. The sub-mammal is a subgraph of the complete mammal-graph. In the Add/Delete parts column, ‘+’n sign is used to show the addition of n number of the molecules, similarly ‘-’n is used to show the removal of n number of molecules. In the table, N is node labels, AN is active node molecules, E is edges, PE is molecule presence on the edge and AE is active molecules on the edge. The [kC] stands for k graph connectedness which is part of only DepQBF experiments.}
